Wetting of the tarsal adhesive fluid controls underwater adhesion in ladybug beetles: Supplementary material

### 2021-05-08 source/tex/supplementary.tex
minor edits in supplementary file
organized supporting info
included evolver script and other relevant files

\title{Wetting of the adhesive fluid controls underwater adhesion in insects: Supplementary material}

@@

\begin{document}
%reset figure/table/equation numbers and include prefix
\renewcommand{\thesection}{S.\arabic{section}}
\setcounter{figure}{0} \renewcommand{\thefigure}{S.\arabic{figure}} 
\setcounter{table}{0} \renewcommand{\thetable}{S.\arabic{table}} 
\setcounter{equation}{0} \renewcommand{\theequation}{S.\arabic{equation}}

@@

bsection{Capillary Bridge Model: Effect of hair diameter at constant fluid
volume}

@@

Pairwise statistical comparison of single leg adhesion force measurements
of the ladybug beetle (\emph{Coccinella septempuctata}) for each contact
type and substrate are shown (Table \ref{tab:Statistical-analysis}).
The uncorrected p-values and Common Language Effect Size (CLES) are
obtained from post-hoc pair-wise Student t-test between A and B while
keeping the third parameter fixed. p-values showing statistically
significant difference between A and B are in boldface. The condition
for statistical significance is based on the Bonferroni-corrected
critical p-value of 0.008.

@@

@@

Capillary force of a single bubble against a PFOTS surface are compared
for two different volumes. The volumes correspond to the expected
range in the case of the trapped bubble in a ladybug. Here, the bubble
is pinned to a micropatterned PDMS substrate on the top. The maximum
adhesion force of any of the bubble never exceeds 50 \textmu N,
significantly lower than the beetle's underwater adhesion to the same
substrate (> 400 \textmu N). Thus, the bubble's contribution
to adhesion in the ``\emph{underwater: bubble}'' contact of a ladybug's
pad should be negligible.

>>>>

\title{Wetting of the tarsal adhesive fluid controls underwater adhesion in ladybug beetles: Supplementary material}

@@

\begin{document}
%reset figure/table/equation numbers and include prefix
\renewcommand{\thesection}{S1.\arabic{section}}
\setcounter{figure}{0} \renewcommand{\thefigure}{S1.\arabic{figure}} 
\setcounter{table}{0} \renewcommand{\thetable}{S1.\arabic{table}} 
\setcounter{equation}{0} \renewcommand{\theequation}{S1.\arabic{equation}}

@@

\section{Capillary Bridge Model: Effect of hair diameter at constant fluid
volume}

@@

Pairwise statistical comparison of single leg adhesion force measurements
of the ladybug beetle (\emph{Coccinella septempuctata}) for each contact
type and substrate are shown (Table \ref{tab:Statistical-analysis}).
The uncorrected p-values and Common Language Effect Size (CLES) are
obtained from post-hoc pair-wise Student t-test between A and B while
keeping the third parameter fixed. p-values showing statistically
significant difference between A and B are in boldface. 
CLES represents the statistical proportion of samples under A with higher adhesion than under B. The condition
for statistical significance is based on the Bonferroni-corrected
critical p-value of 0.008.

@@

\section{Field desorption mass spectroscopy}

To test whether the ladybug beetles retain
their adhesive fluid underwater unchanged, we performed a Field Desorption Mass Spectroscopy
(FDMS) using a ZAB 2-SE-FPD spectrometer (VG Instruments, Malaysia). The measurements
were done on the extracted secretions before and after submerging its
legs under water. The middle leg of an Asian ladybird (\emph{Harmonia
axyridis}) was immersed in 50 \textmu L Tetrahydrofuran (THF) for 20 min and then transferred
to the measurement chamber of the FDMS. As a reference, pure THF was
used. The second middle leg of the same ladybird was subsequently
immersed in 100 \textmu L Milli-Q water for 15 min (close to the time-scale of the underwater adhesion tests), then in THF for
20 min and then transferred to the measurement chamber of the spectrometer.
Molecular weights were extracted from the peak positions of the
FDMS spectra. Probable compostion was identified from the molecular weights by assuming the secretion fluid consists possibly of hydrocarbons, alcohols, aldehydes or carboxylic acids.

FDMS results confirm the presence of adhesive fluid on the Asian ladybird's
leg when underwater (Table \ref{tab:Molecular-distribution-of}).
Molecular weights of the epicuticular grease extracted from the beetle’s leg, without and after immersion in water, show that, except
for two molecular weights (406.8 g mol\protect\textsuperscript{-1} and 331.6 g mol\protect\textsuperscript{-1}), the chemical
fingerprint remained unchanged. This let us assume that the tarsal adhesive fluid
was not washed away underwater. Probable compounds in the fluid, corresponding
to the resultant molecular weights, include mostly aliphatic hydrocarbons
with traces of aldehydes. Our preliminary measurements on \emph{Harmonia axyridis} let us conjecture that, 
even for the case of \emph{Coccinella septempuctata}, the tarsal adhesive fluid was not washed away from the hairs during the underwater experiments. A detailed study is however essential to ensure that the difference in the ladybug species between our adhesion and FDMS tests doesn't qualitatively change the above outcome. Further, the detected compounds would also include cuticular secretions from the leg apart from the tarsal fluid. Thus, a more precise fluid extraction method is necessary to definitely confirm the above conjecture, and will be a subject of future study.

\begin{table}[H]
\centering{}%
\begin{tabular}{|c|c|c|}
\hline 
Without submerging (g mol\protect\textsuperscript{-1}) & After submerging (g mol\protect\textsuperscript{-1}) & Probable compounds\tabularnewline
\hline 
\hline 
324.5 & 324.5 & C\textsubscript{23}H\textsubscript{48}, C\textsubscript{22}H\textsubscript{44}O\tabularnewline
\hline 
 & 331.6 & C\textsubscript{24}H\textsubscript{44}\tabularnewline
\hline 
350.5 & 350.5 & C\textsubscript{25}H\textsubscript{50}\tabularnewline
\hline 
352.5 & 352.5 & C\textsubscript{25}H\textsubscript{52}, C\textsubscript{24}H\textsubscript{48}O\tabularnewline
\hline 
378.5 & 378.5 & C\textsubscript{27}H\textsubscript{54}\tabularnewline
\hline 
404.6 & 404.5 & C\textsubscript{29}H\textsubscript{56}\tabularnewline
\hline 
406.8 &  & C\textsubscript{29}H\textsubscript{58}\tabularnewline
\hline 
432.8 & 432.7 & C\textsubscript{31}H\textsubscript{60}\tabularnewline
\hline 
\end{tabular}\caption{Molecular weights of the tarsal adhesive fluid secretion of \emph{Harmonia axyridis}
without and after submerging the beetle's leg in water. \label{tab:Molecular-distribution-of}}
\end{table}

@@

Capillary force of a single bubble against a PFOTS surface are compared
for two different volumes. The volumes correspond to the expected
range in the case of the trapped bubble in a ladybug. Here, the bubble
is pinned to a micropatterned PDMS substrate on the top. The maximum
adhesion force of any of the bubble never exceeds 50 \textmu N,
significantly lower than the beetle's underwater adhesion to the same
substrate (> 400 \textmu N). Thus, the bubble's contribution
to adhesion in the ``\emph{underwater: bubble}'' contact of a ladybug's
pad should be negligible. Measurement videos are included in the supplementary material (S6).
